\begin{thebibliography}{10}
%uvod
\bibitem{hotcloud}
	\emph{Remzi H a Andrea C. Arpaci-Dusseau. Cloud-native file systems. 10th Workshop on Hot Topics in Cloud Computing [online]. 2018, 2018, , 1 [cit. 2019-04-15]. Dostupné z: \url{https://www.usenix.org/system/files/conference/hotcloud18/hotcloud18-paper-arpaci-dusseau.pdf}}
%cloud computing
\bibitem{ZHANG}
	\emph{ZHANG, Shuai, Shufen ZHANG, Xuebin CHEN a Xiuzhen HUO. Cloud Computing Research and Development Trend. In: 2010 Second International Conference on Future Networks [online]. IEEE, 2010, 2010, s. 93-97 [cit. 2019-04-21]. DOI: 10.1109/ICFN.2010.58. ISBN 978-1-4244-5666-6. Dostupné z: \url{http://ieeexplore.ieee.org/document/5431874/}}

\bibitem{bohm2010cloud}
	\emph{BÖHM, MARKUS, STEFANIE LEIMEISTER, CHRISTOPH RIEDL a HELMUT KRCMAR. Cloud Computing and Computing Evolution. Technische Universitat Munchen (TUM), Germany [online]. 2010, 2010 [cit. 2018-12-15]. Dostupné z: \url{https://s3.amazonaws.com/academia.edu.documents/7299069/05431874.pdf?AWSAccessKeyId=AKIAIWOWYYGZ2Y53UL3A&Expires=1555886954&Signature=4WW794UtzhnRNy7d21b0CaBPEWo\%3D&response-content-disposition=inline\%3B\%20filename\%3DCloud_computing_research_and_development.pdf}}

\bibitem{cc2011principles}
	\emph{BUYYA, Rajkumar, James BROBERG a Andrzej GOŚCIŃSKI. Cloud computing: principles and paradigms. Hoboken, N.J.: Wiley, c2011. ISBN 978-0-470-88799-8.}

\bibitem{mel2011nist}
	\emph{Mell, Peter and Grance, Tim and others. The NIST definition of cloud computing. Computer Security Division, Information Technology Laboratory, National Institute of Standards and Technology Gaithersburgb [online]. 2011, 2010 [cit. 2018-12-15]. Dostupné z: \url{http://faculty.winthrop.edu/domanm/csci411/Handouts/NIST.pdf}}

\bibitem{Vaquero-cloud-definition}
	\emph{Luis M. Vaquero, Luis Rodero-Merino, Juan Caceres a Maik Lindner. A Break in the Clouds: Towards a Cloud Definition. ACM SIGCOMM Computer Communication Review [online]. 2009, 2009, 39(1) [cit. 2018-12-17]. Dostupné z: \url{http://faculty.winthrop.edu/domanm/csci411/Handouts/NIST.pdf}}

\bibitem{Ambrust2009}
	\emph{Michael Armbrust, Armando Fox, Rean Griffith, Anthony D. Joseph, Randy Katz a Andy Konwinski. Above the Clouds: A Berkeley View of Cloud Computing. Electrical Engineering and Computer Sciences University of California at Berkeley [online]. 2009, 2009 [cit. 2018-12-17]. Dostupné z: \url{https://www2.eecs.berkeley.edu/Pubs/TechRpts/2009/EECS-2009-28.pdf}}


\bibitem{murphy2017virtualization}
	\emph{Alan Murphy. WHITE PAPER Virtualization Defined - Eight Different Ways [online]. 2007, 2007 [cit. 2018-12-17]. Dostupné z: \url{https://worldtechit.com/wp-content/uploads/2015/07/f5-white-paper-virtualization-defined-eight-different-ways-.pdf}}


\bibitem{devopsonline}
	\emph{Leah Alger. HSBC’s journey with Amazon Cloud. DevOps Online [online]. Velká Británie, 2018 [cit. 2018-12-20]. Dostupné z: \url{http://www.devopsonline.co.uk/hsbcs-journey-with-amazon-cloud/}}

\bibitem{digitalnewasia}
	\emph{Edwin Yapp. Culture shift imperative in cloud adoption: HSBC CIO. Digital News Asia [online]. 2017 [cit. 2018-12-20]. Dostupné z: \url{https://www.digitalnewsasia.com/business/culture-shift-imperative-cloud-adoption-hsbc-cio}}

%end cloud computing

% cloud native chapter03
\bibitem{BRUNNER}
	\emph{, Sandro Brunner, Martin Blöchlinger, Giovanni Toffetti, Josef Spillner, Thomas Michael Bohnert. Experimental Evaluation of the Cloud-Native Application Design. 2015 IEEE/ACM 8th International Conference on Utility and Cloud Computing (UCC) [online]. IEEE, 2015 [cit. 2019-01-07]. Dostupné z: \url{https://digitalcollection.zhaw.ch/bitstream/11475/7419/1/cnaeval-archive.pdf}}

\bibitem{petsvscattle}
	\emph{BIAS, Randy. The History of Pets vs Cattle and How to Use the Analogy Properly. Cloud scaling [online]. 29 Sep 2016 [cit. 2019-01-07]. Dostupné z: \url{http://cloudscaling.com/blog/cloud-computing/the-history-of-pets-vs-cattle/}}

\bibitem{CNCFdefinition}
	\emph{CNCF Cloud Native Definition v1.0. Cloud native computing foundation github [online]. 11 Jun 2018 [cit. 2019-01-07]. Dostupné z: \url{https://github.com/cncf/toc/blob/master/DEFINITION.md}}

\bibitem{KRATZKE}
	\emph{NANE KRATZKE a PETER-CHRISTIAN QUINT. Understanding cloud-native applications after 10 years of cloud computing - A systematic mapping study. The Journal of Systems and Software [online]. 2017, 126 [cit. 2019-04-22]. Dostupné z: \url{https://www.researchgate.net/profile/Nane_Kratzke/publication/312045183_Understanding_Cloud-native_Applications_after_10_Years_of_Cloud_Computing_-_A_Systematic_Mapping_Study/links/588202be4585150dde401522/Understanding-Cloud-native-Applications-after-10-Years-of-Cloud-Computing-A-Systematic-Mapping-Study.pdf}}


\bibitem{uber}
	\emph{HADDAD, Einas. Service-Oriented Architecture: Scaling the Uber Engineering Codebase As We Grow. Uber Engineering [online]. 2015 [cit. 2019-01-15]. Dostupné z: \url{https://eng.uber.com/soa/}}

\bibitem{soundcloud}
	\emph{CALCADO, Phil. Building Products at SoundCloud —Part I: Dealing with the Monolith. SoundCloud developers [online]. 2014 [cit. 2019-01-15]. Dostupné z: \url{https://developers.soundcloud.com/blog/building-products-at-soundcloud-part-1-dealing-with-the-monolith}}


\bibitem{groupon}
	\emph{GEITGEY, Adam. I-Tier: Dismantling the Monolith. Groupon Engineering [online]. 2013 [cit. 2019-01-15]. Dostupné z: \url{https://engineering.groupon.com/2013/misc/i-tier-dismantling-the-monoliths/}}

\bibitem{chaosmonkey}
	\emph{Netflix/ChaosMonkey. Netflix GitHub [online]. 2019 [cit. 2019-01-18]. Dostupné z: \url{https://github.com/Netflix/chaosmonkey}}

\bibitem{googleMonolith}
	\emph{WU, Andy. White Paper - Taking the Cloud-Native Approach with Microservices [online]. In: . [cit. 2019-01-20]. Dostupné z: \url{https://cloud.google.com/files/Cloud-native-approach-with-microservices.pdf}}

\bibitem{balalaieMicroservies}
	\emph{ARMIN BALALAIE, ABBAS HEYDARNOOR a POOYAN JAMSHID. Migrating to Cloud-Native Architectures Using Microservices: An Experience Report. BALALAIE, Armin; HEYDARNOORI, Abbas; JAMSHIDI, Pooyan. Migrating to cloud-native architectures using microservices: an experience report. In: European Conference on Service-Oriented and Cloud Computing [online]. Springer, 2015 [cit. 2019-01-20]. Dostupné z: \url{https://arxiv.org/pdf/1507.08217.pdf}}

\bibitem{sleethrift}
	\emph{SLEE, Mark, Aditya AGARWAL a Marc KWIATKOWSKI. Thrift: Scalable Cross-Language Services Implementation. Facebook White Paper [online]. 2007 [cit. 2019-01-20]. Dostupné z: \url{https://users.cs.jmu.edu/bernstdh/Web/CS462/thrift-20070401.pdf}}

\bibitem{docsopenshift}
	\emph{OpenShift Enterprise Documentation. Red Hat OpenShift [online]. 2019 [cit. 2019-01-26]. Dostupné z: \url{https://docs.openshift.com/enterprise/3.0/architecture/core_concepts/containers_and_images.html}}

\bibitem{lxc}
	\emph{What's LXC?. Linux containers [online]. 2019 [cit. 2019-01-26]. Dostupné z: \url{https://linuxcontainers.org/lxc/introduction/}}

\bibitem{rkt}
	\emph{Rkt overview. CoreOS [online]. 2019 [cit. 2019-01-26]. Dostupné z: \url{https://coreos.com/rkt/}}

\bibitem{docker}
	\emph{Docker [online]. 2019 [cit. 2019-01-26]. Dostupné z: \url{https://www.docker.com/}}

\bibitem{picture}
	\emph{Docker container use adoption devops clusterhq survey. In: Nanobox [online]. 16 Jun 2017 [cit. 2019-01-26]. Dostupné z: \url{https://content.nanobox.io/content/images/2017/06/docker-container-use-adoption-devops-clusterhq-survey.png}}
	
\bibitem{docker-security}
	\emph{COMBE, Theo, Antony MARTIN a Roberto DI PIETRO. To Docker or Not to Docker: A Security Perspective. IEEE Cloud Computing [online]. 2016, 3(5), 54-62 [cit. 2019-01-23]. DOI: 10.1109/MCC.2016.100. ISSN 2325-6095. Dostupné z: \url{http://ieeexplore.ieee.org/document/7742298/}}

\bibitem{picture-docker-layers}
	\emph{Docker Containers - Talk Linux Day. In: SlideShare [online]. 20 Jun 2016 [cit. 2019-02-10]. Dostupné z: \url{https://image.slidesharecdn.com/dockercontainerslinuxday2015-160620093427/95/docker-containers-talk-linux-day-2015-15-638.jpg?cb=1466415275}}

\bibitem{namespaces}
	\emph{Namespaces - overview of Linux namespaces. Linux man pages online [online]. 2019 [cit. 2019-01-23]. Dostupné z: \url{http://man7.org/linux/man-pages/man7/namespaces.7.html}}

\bibitem{cgroup}
	\emph{Cgroups - Linux control groups. Linux man pages online [online]. 2019 [cit. 2019-01-23]. Dostupné z: \url{http://man7.org/linux/man-pages/man7/cgroups.7.html}}

\bibitem{ROCKET}
	\emph{MARTIN, John Paul, A. KANDASAMY a K. CHANDRASEKARAN. Exploring the support for high performance applications in the container runtime environment. Human-centric Computing and Information Sciences [online]. 2018, 8(1) [cit. 2019-04-22]. DOI: 10.1186/s13673-017-0124-3. ISSN 2192-1962. Dostupné z: \url{https://hcis-journal.springeropen.com/articles/10.1186/s13673-017-0124-3}}

\bibitem{selinux}
	\emph{Rkt and SELinux. Rkt GitHub page [online]. [cit. 2019-01-25]. Dostupné z: \url{https://github.com/rkt/rkt/blob/master/Documentation/selinux.md}}

\bibitem{oci}
	\emph{About Open Container Iniciative. Open container iniciative [online]. 2019 [cit. 2019-02-02]. Dostupné z: \url{https://www.opencontainers.org/about}}


\bibitem{runtimespec}
	\emph{Open Container Initiative Runtime Specification. OpenContainer GitHub page [online]. 2019 [cit. 2019-02-02]. Dostupné z: \url{https://github.com/opencontainers/runtime-spec/blob/master/spec.md}}

\bibitem{imagespec}
	\emph{Image Format Specification. OpenContainer GitHub page [online]. 2019 [cit. 2019-02-02]. Dostupné z: \url{https://github.com/opencontainers/image-spec/blob/master/spec.md}}

%orchestratory
\bibitem{container-orchestration}
	\emph{ELDRIDGE, Isaac. What Is Container Orchestration?. New Relic [online]. 17 Jul 2018 [cit. 2019-02-08]. Dostupné z: \url{https://blog.newrelic.com/engineering/container-orchestration-explained/}}

\bibitem{sysdig}
	\emph{CARTER, Eric. 2018 Docker Usage Report. Sysdig [online]. 29 May 2018 [cit. 2019-02-08]. Dostupné z: \url{https://sysdig.com/blog/2018-docker-usage-report/}}

\bibitem{delvalle}
	\emph{RENAN DELVALLE, PRADYUMNA KAUSHIK, ABHISHEK JAIN, JESSICA HARTOG, AND MADHUSUDHAN GOVINDARAJU. Owards Efficient Resource Management on Heterogeneous Clusters with Apache Mesos. 2017 IEEE 10th International Conference on Cloud Computing (CLOUD) [online]. IEEE, 2017, , 262-269 [cit. 2019-02-10]. Dostupné z: \url{http://cloud.cs.binghamton.edu/wordpress/wp-content/uploads/2017/07/electron-1.pdf}}

\bibitem{mesos-picture}
	\emph{LUPO, Gianluca. Setup Mesos on a single node. In: Swiss push [online]. 5 Dec 2014 [cit. 2019-02-10]. Dostupné z: \url{http://www.swisspush.org/assets/images/mesos/mesos-1.png}}

\bibitem{marathon}
	\emph{Marathon Docs. Mesos Sphere [online]. [cit. 2019-02-20]. Dostupné z: \url{https://mesosphere.github.io/marathon/}}

\bibitem{k8s-architecture}
	\emph{KAPOOR, Sandhya. How Watson Health Cloud Deploys Applications with Kubernetes. In: Kubernetes blog [online]. 14 Jul 2017 [cit. 2019-02-26]. Dostupné z: \url{https://lh3.googleusercontent.com/EU3DgtFKagWp5S0UpKj-wRgx8WK2nvQ2BG-4dGio57pGNj42A7Lip9IARBba34hIm84-_7zwWt6iImQE8beSqLxpzXm-2w_84M_X2IHQ7jvpWtIDMF81hmq6N4hGSxp6DQoFW5qX}}

\bibitem{calico}
	\emph{Calico for Kubernetes. Project Calico [online]. 2019 [cit. 2019-02-26]. Dostupné z: \url{https://docs.projectcalico.org/v2.0/getting-started/kubernetes/}}

\bibitem{flanel}
	\emph{Flannel. CoreOS GitHub page [online]. [cit. 2019-02-26]. Dostupné z: \url{https://github.com/coreos/flannel}}

\bibitem{weave}
	\emph{Run Weave Net with Kubernetes in Just One Line. Weaveworks [online]. 27 Sep 2016 [cit. 2019-02-26]. Dostupné z: \url{https://www.weave.works/blog/weave-net-kubernetes-integration/}}

%Edge chapter
\bibitem{buyya}
	\emph{BUYYA, Rajkumar a Satish Narayana SRIRAMA. Fog and edge computing: principles and paradigms. Hoboken, NJ, USA: John Wiley & Sons, 2019. ISBN 9781119524984.}

\bibitem{akraino}
	\emph{GRIMBERG, Andrew. Akraino Wiki Page. Akraino Edge stack [online]. 22 Feb 2019 [cit. 2019-03-06]. Dostupné z: \url{https://wiki.akraino.org/}}

\bibitem{chick-1}
	\emph{CHAMBERS, Brian, Caleb HURD a Alex CRANE. Bare Metal K8s Clustering at Chick-fil-A Scale. In: Medium [online]. 26 Jun [cit. 2019-03-07]. Dostupné z: \url{https://medium.com/@cfatechblog/bare-metal-k8s-clustering-at-chick-fil-a-scale-7b0607bd3541}}

\bibitem{chick-2}
	\emph{CHAMBERS, Brian, Caleb HURD, Alex CRANE, Morgan MCENTIRE, Jamie ROBERTS a Laura JAUHCH. Edge Computing at Chick-fil-A. In: Medium [online]. 30 Jul 2018 [cit. 2019-03-07]. Dostupné z: \url{https://medium.com/@cfatechblog/edge-computing-at-chick-fil-a-7d67242675e2}}

\bibitem{chick-3}
	\emph{SCHAEFER, Keith a Alain NICOLET. Edge AI in a Smarter Chick-fil-A. In: Medium [online]. 22 Oct 2018 [cit. 2019-03-07]. Dostupné z: \url{https://medium.com/@cfatechblog/edge-ai-in-a-smarter-chick-fil-a-6e56fe026154}}


\bibitem{goyal2014public}
	\emph{GOYAL, Sumit. Public vs Private vs Hybrid vs Community - Cloud Computing: A Critical Review. International Journal of Computer Network and Information Security [online]. 2014, 6(3), 20-29 [cit. 2019-04-22]. DOI: 10.5815/ijcnis.2014.03.03. ISSN 20749090. Dostupné z: \url{http://www.mecs-press.org/ijcnis/ijcnis-v6-n3/v6n3-3.html}}

\bibitem{google-edge}
	\emph{Hybrid and Multi-Cloud Architecture Patterns. Google cloud solutions [online]. 24 Oct 2018 [cit. 2019-03-15]. Dostupné z: \url{https://cloud.google.com/solutions/hybrid-and-multi-cloud-architecture-patterns}}

\bibitem{edge-picture}
	\emph{Hybrid multi cloud pattern edge hybrid. In: Google cloud solutions [online]. [cit. 2019-03-15]. Dostupné z: \url{https://cloud.google.com/solutions/images/hybrid-multi-cloud-pattern-edge-hybrid.svg}}

\bibitem{manageiq}
	\emph{ManageIQ Documentation. ManageIQ [online]. 2019 [cit. 2019-03-20]. Dostupné z: \url{http://manageiq.org/docs/}}

\bibitem{lwn}
	\emph{JANSEN, Geert. Managing heterogeneous environments with ManageIQ. LWM.net [online]. 16 Mar 2016 [cit. 2019-03-20]. Dostupné z: \url{https://lwn.net/Articles/680060/}}

\bibitem{cf}
	\emph{Cloud Foundry Overview. Cloud Foundry [online]. 2019 [cit. 2019-03-23]. Dostupné z: \url{https://docs.cloudfoundry.org/concepts/overview.html}}

\bibitem{garden}
	\emph{Garden-runC Release. Cloud Foundry GitHub page [online]. 2019 [cit. 2019-03-23]. Dostupné z: \url{https://github.com/cloudfoundry/garden-runc-release}}

\bibitem{pivotal}
	\emph{Pivotal Cloud Foundry documentation. Pivotal Cloud Foundry [online]. 2019 [cit. 2019-03-23]. Dostupné z: \url{https://docs.pivotal.io/pivotalcf/2-4/pas/intro.html}}

\bibitem{bosh}
	\emph{Cloud foundry BOSH get started. Cloud Foundry BOSH [online]. 2019 [cit. 2019-03-23]. Dostupné z: \url{https://www.cloudfoundry.org/get-started/}}

\bibitem{mistio}
	\emph{Mist.io getting started. Mist.io [online]. 2019 [cit. 2019-03-25]. Dostupné z: \url{https://docs.mist.io/category/3-getting-started}}

\bibitem{federace}
	\emph{REHMAN, Irfan Ur, Paul MORIE a Shashidhara TD. Kubernetes Federation Evolution. Kubernetes blog [online]. 12 Dec 2018 [cit. 2019-03-28]. Dostupné z: \url{https://kubernetes.io/blog/2018/12/12/kubernetes-federation-evolution/}}

\bibitem{federace-picture}
	\emph{Kubernetes federation. Kubernetes blog [online]. 2018 [cit. 2019-03-28]. Dostupné z: \url{https://raw.githubusercontent.com/kubernetes-sigs/federation-v2/master/docs/images/concepts.png}}

\bibitem{netflix-spinnaker}
	\emph{Global Continuous Delivery with Spinnaker. Medium, Neflix technology blog [online]. 16 Nov 2015 [cit. 2019-03-30]. Dostupné z: \url{https://medium.com/netflix-techblog/global-continuous-delivery-with-spinnaker-2a6896c23ba7}}

\bibitem{waze}
	\emph{FEINER, Tom, Katriel TRAUM, Nir TARCIC a Matt DUFTLER. Guest post: Multi-Cloud continuous delivery using Spinnaker at Waze. Google cloud blog [online]. 16 Feb 2017 [cit. 2019-03-30]. Dostupné z: \url{https://cloud.google.com/blog/products/gcp/guest-post-multi-cloud-continuous-delivery-using-spinnaker-at-waze}}

\bibitem{spinnaker}
	\emph{Spinnaker concepts. Spinnaker [online]. 2019 [cit. 2019-03-31]. Dostupné z: \url{https://www.spinnaker.io/concepts/}}

\bibitem{k8sauth}
	\emph{Authorization Overview. Kubernetes documentation [online]. 2019 [cit. 2019-04-02]. Dostupné z: \url{https://kubernetes.io/docs/reference/access-authn-authz/authorization/}}

\bibitem{miek}
	\emph{GIEBEN, Miek. Learning Go [online]. 2018 [cit. 2019-04-07]. Dostupné z: \url{https://miek.nl/go/}}

\bibitem{local-cluster}
	\emph{Getting started locally. Kubernetes community GitHub page [online]. 2017 [cit. 2019-04-07]. Dostupné z: \url{https://github.com/kubernetes/community/blob/master/contributors/devel/running-locally.md#starting-the-cluster}}

\bibitem{MASTERING-KUBERNETES}
	\emph{SAYFAN, Gigi. Mastering Kubernetes [online]. Second edition. Birmingham: Packt publishing, 2018 [cit. 2019-04-05]. ISBN 978-1-78899-978-6.}
\end{thebibliography}

